---
title: "Logicals"
author: "Julia Parish"
date: "8/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

```

## Taking a look at `starwars`

- `include = ` show or hide everything
- `echo = ` : show or hide code


```{r, include = FALSE}
# summary of starwars

summary(starwars)

# look at first few lines
head(starwars)

# check out dimensions
dim(starwars)

```
```{r, eval = FALSE}
ggplot(data = starwars, aes(x = height, y = mass)) + 
  geom_point(color = "purple")
```

## Find the mean, variance, & SD of character heights
default in R is if there are MIA values, then the default is NA when running a function (na.rm = FALSE)

```{r}
sw_height_mean <- mean(starwars$height, na.rm = TRUE)
sw_height_mean

```
# Using a similar naming system, find: 
# Variance of character height (var())
# Standard deviation of character height (sd())

```{r}
sw_height_var <- var(starwars$height, na.rm = TRUE)
sw_height_var

sw_height_sd <- sd(starwars$height, na.rm = TRUE)
sw_height_sd

```

# In line R Code

Mean character height is `r round(sw_height_mean, 1)` cm, with a standard deviation of `r round(sw_height_sd, 1)` cm.

# Logical expressions

```{r}
5 < 10

"cat" > "armadillo"

"cat" > "elephant"

"cats" > "cat"
 
"dog" == "dog"

```
```{r}

10 <= 11

5 >= 4

```

```{r}
tarantulas <- c(1,3,7,10,15)

tarantulas > 5

```
## Logical operators:

- `!`
- `&`
- `|`


```{r}
3 < 1 | 8 > 2

6 < 10 & 5 < 1

7 != 11

4 != 4 | 2 < 5 | 6 > 10

0 == TRUE

0 == FALSE

1 == TRUE

```

